Extending the WebID Protocol with Access Delegation

### 2012-09-06 paper.tex

\institute{
Universit\"at Leipzig, Institut f\"ur Informatik, AKSW,\\
Postfach 100920, D-04009 Leipzig, Germany,\\
\email{\{lastname\}@informatik.uni-leipzig.de}\\
\url{http://aksw.org/FirstnameLastname} (WebID)
\medskip\and
Apache Foundation\\ 
\email{henry.story@bblfish.net}\\
\url{http://bblfish.net/people/henry/card\#me} (WebID)
\medskip\and
CNRS Samovar UMR 5157, TELECOM SudParis\\
\email{andrei.sambra@it-sudparis.eu}\\
\url{https://my-profile.eu/people/deiu/card\#me} (WebID)
}

@@

As two real-world examples we describe two different implementations where WebID delegation is deployed and needed.
MyProfile is WebID profile service application and OntoWiki a semantic data wiki.

\textbf{MyProfile}\footnote{\url{http://myprofile-project.org/}}
is a web server demonstrating how easy it is to create a WebID profile, and buidling up some distributed social web applications upon this.
Its main purpose is to provide a unified user account, or simply \textit{user profile}.
Currently these are tied to the my-profile-project web site, but it has been architect from the ground up to work with distributed Linked Data, making it then easy to dissociate the software stack from the myprofile-project domain name, and allowing it to be deployed on a machine under the user's control, preferably even a device located within the user physical reach.

>>>>

\institute{
Universit\"at Leipzig, Institut f\"ur Informatik, AKSW,\\
Postfach 100920, D-04009 Leipzig, Germany,\\
\email{\{lastname\}@informatik.uni-leipzig.de}\\
\url{http://aksw.org/FirstnameLastname} (WebID)
\medskip\and
Apache Foundation\\ 
\email{henry.story@bblfish.net}\\
\url{http://bblfish.net/people/henry/card\#me} (WebID)
\medskip\and
CNRS Samovar UMR 5157, Institut Mines-Telecom / Telecom SudParis\\
\email{andrei.sambra@it-sudparis.eu}\\
\url{https://my-profile.eu/people/deiu/card\#me} (WebID)
}

@@

As two real-world examples we describe two different implementations where WebID delegation is deployed and needed.
MyProfile is a WebID identity service application and OntoWiki a semantic data wiki.

\textbf{MyProfile}\footnote{\url{http://myprofile-project.org/}}
is a web service demonstrating how easy it is to create a WebID profile, and also building up distributed social web applications upon it.
Its main purpose is to provide a unified user account, or simply \textit{user profile}.
Currently these are tied to the MyProfile project web site, but it has been designed from the ground up to work with distributed Linked Data, making it then easy to dissociate the software stack from the MyProfile project domain name, allowing it to be deployed on a machine under the user's control, preferably even a device located within the user physical reach.
